Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-10-18 manuscripts/manuscript.Rmd
add snowy grouper data;

```{r Figure_1, fig.cap="ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
tuna <- read.csv("components/data/tuna.csv")
tuna <- melt(tuna, id="year")
ggplot(tuna, aes(year, value)) + geom_point() +
  facet_wrap(~variable, ncol=1, scale="free_y") + 
  ylab("Bluefin Tuna harvest (tonnes)") + theme_bw()
```

>>>>

```{r Figure_1, fig.cap="ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
ex_long <- gather(ex, variable, value, year, species)

ggplot(ex_long, aes(year,value)) + 
  geom_line() + geom_point() + 
  facet_wrap(variable~species, scales="free") + 
  ylab("value (mt)") + theme_bw()
```
